Precision line-by-line forward models for \'echelle spectra

### 2022-08-12 paper/paper1/ms.tex
Tiny fixes to appendix

We currently assume the input spectra are adequately normalized to the continuum.  We have a few options to relax this assumption.  We could  simply tune the $\mathsf{P}$ term that represents the wavelength-dependent pre-factor to Equation \ref{equation1}.  Tuning $\mathsf{P}$ would correct for large-scale imperfections in the otherwise-fixed continuum flattening procedure.  This change would be easy and effective, but has some challenge with model selection and flexibility: how to set the polynomial order to avoid over- and under-fitting.  Gaussian Processes (GPs) offer many advantages for continuum fitting \citet{czekala15}.  In short, a GP-likelihood relaxes the assumption that the continuum has been perfectly normalized, in favor of the more realistic statement ``the continuum has been coarsely normalized, with some characteristic-but-as-yet-unknown correlation and scale length and amplitude of the imperfections''.  That statement translates to the following modification to Equation \ref{simpleLikelihood}:

@@

where we introduce the covariance matrix $\mathsf{C}$, with its associated kernel and collection of typically 2-3 parameters.  We anticipate that this GP likelihood would have the greatest impact on stellar stars with significant band-heads and line-blanketing: spectra with a so-called ``pseudo-continuum''.  M-dwarfs and brown dwarfs fall into this challenging category.

@@

There exists at least a few demerits of adopting the line lists, and therefore supporting the \emph{blase} strategy.  First, these line lists need to undergo expensive multi-level radiative transfer calculations in order to obtain their amplitudes, so adopting the line lists would mean a laborious and computationally expensive pursuit simply to get close to what has already been computed.  Second, as the effective temperature scales to ultracool dwarfs (Figure \ref{fig_Nlines_vs_teff}) the number of lines sky-rockets, tending towards the billions for T-dwarfs.  The methane line list alone \citep{2020ApJS..247...55H} represents a prohibitive data volume.  The ExoJAX and Radis \cite{2019JQSRT.222...12P,2021JQSRT.26107476V} libraries offer a breakthrough solution to the voluminous line list problem.  Even still, \emph{blase} deals with the less pure but more practical ``pseudo line'' that gets closer to the astronomical observables anyways, and offers a middle ground between the extremes of interpretability and performance.

@@

\emph{``Transfer-transfer learning''}
To-be-completed

>>>>

We currently assume the input spectra are adequately normalized to the continuum.  We have a few options to relax this assumption.  We could  simply tune the $\mathsf{P}$ term that represents the wavelength-dependent pre-factor to Equation \ref{equation1}.  Tuning $\mathsf{P}$ would correct for large-scale imperfections in the otherwise-fixed continuum flattening procedure.  This change would be easy and effective, but has some challenge with model selection and flexibility: how to set the polynomial order to avoid over- and under-fitting.  Gaussian Processes (GPs) offer many advantages for continuum fitting \citep{czekala15}.  In short, a GP-likelihood relaxes the assumption that the continuum has been perfectly normalized, in favor of the more realistic statement ``the continuum has been coarsely normalized, with some characteristic-but-as-yet-unknown correlation and scale length and amplitude of the imperfections''.  That statement translates to the following modification to Equation \ref{simpleLikelihood}:

@@

where we introduce the covariance matrix $\mathsf{C}$, with its associated kernel and collection of typically 2-3 parameters.  We anticipate that this GP likelihood would have the greatest impact on stars with significant band-heads and line-blanketing: spectra with a so-called ``pseudo-continuum''.  M-dwarfs and brown dwarfs fall into this challenging category.

@@

As already emphasized, there exist at least a few demerits of adopting the line lists, and therefore supporting the \emph{blase} strategy.  First, these line lists need to undergo expensive multi-level radiative transfer calculations in order to obtain their amplitudes, so adopting the line lists would mean a laborious and computationally expensive pursuit simply to get close to what has already been computed.  Second, as the effective temperature scales to ultracool dwarfs (Figure \ref{fig_Nlines_vs_teff}) the number of lines sky-rockets, tending towards the billions for T-dwarfs.  The methane line list alone \citep{2020ApJS..247...55H} represents a prohibitive data volume.  The ExoJAX and Radis \citep{2019JQSRT.222...12P,2021JQSRT.26107476V} libraries offer a breakthrough solution to the voluminous line list problem.  Even still, \emph{blase} deals with the less pure but more practical ``pseudo line'' that gets closer to the astronomical observables anyways, and offers a middle ground between the extremes of interpretability and performance.

@@
